Stat 400 Project

### 2021-12-07 Stat 400 proj.Rmd
Created a plot of the people's positions and infection status

>>>>

```{r}
simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
  end_day <- list()
  num_cases <- rep(NA, days)
  num_cases <- c(I_0, num_cases)
  num_new_cases <- rep(NA, days)

    }
  }
  return(end_day)
}
days <- simulator22(20, 5, 1, 1, 1, 0.2)
days

ggplot() +
  geom_point(aes(x=days[[20]][, 'x'], y= days[[20]][, 'y'], color=days[[20]][, 'subjects']))
```
